Contribution Title\thanks{Supported by organization x.}

### 2019-10-23 paper/paper.tex
Fixed messed up figures

@@

Consider the following OCaml example of nested \verb|match| expressions, as stated by \cite{palmkvistCreatingDomainSpecificLanguages2019}).

\begin{minipage}{.35\textwidth}
\begin{lstlisting}[language={[objective]caml},numbers=left]
match 1 with
  | 1 -> match "one" with
         | str -> str
  | 2 -> "two"
\end{lstlisting}
\end{minipage}
\vrule
\begin{minipage}{\textwidth}
\begin{lstlisting}
  File "./nestmatch.ml", line 4, characters 4-5:
  Error: This pattern matches values of type int
         but a pattern was expected which
         matches values of type string
\end{lstlisting}
\end{minipage}

@@

\begin{minipage}{\textwidth}
\begin{lstlisting}[language={[objective]caml},numbers=left]
match 1 with
  | 1 -> (match "one" with
          | str -> str)
  | 2 -> "two"
\end{lstlisting}
\end{minipage}

@@

\begin{itemize}
\item Visibly pushdown languages with the same input partitions are closed under intersection, complement, and union \cite{alurVisiblyPushdownLanguages2004}. Intersection is given by a product automaton. Given a pair of VPDAs $(Q_1, \T, \delta_1, q_0, F_1)$ and $(Q_2, \T, \delta_2, q'_0, F_2)$ their product automaton has the form $(Q_1 \times Q_2, \T, \delta', (q_0, q'_0), F_1 \times F_2)$ where:
  $$
  \begin{array}{r@{\ =\ }ll}
    \delta'((p_1, p_2), c, \lambda) & \{((q_1, q_2), (g_1, g_2)) \mid (q_1, g_1) \in \delta_1(p_1, c, \lambda), (q_2, g_2) \in \delta_2(p_2, c, \lambda) \} & \!\!\!\!\text{where } c \in \T_c \\
    \delta'((p_1, p_2), i, \lambda) & \{((q_1, q_2), \lambda) \mid (q_1, \lambda) \in \delta_1(p_1, i, \lambda), (q_2, \lambda) \in \delta_2(p_2, i, \lambda) \} & \!\!\!\!\text{where } i \in \T_i \\
    \delta'((p_1, p_2), r, (g_1, g_2)) & \{((q_1, q_2), \lambda) \mid (q_1, \lambda) \in \delta_1(p_1, r, \lambda), (q_2, \lambda) \in \delta_2(p_2, r, \lambda) \} & \!\!\!\!\text{where } r \in \T_r \\
  \end{array}
  $$

@@

\begin{figure}
\centering
\begin{minipage}{.47\textwidth}
  \centering
  \begin{tabular}{@{}ll@{}}
      Terminals & $t \in \T$ \\
      Non-terminals & $N \in \NT$ \\
      Labels & $l \in \Labels$ \\
      \multicolumn{2}{@{}l@{}}{$\T$, $\NT$, and $\Labels$ disjoint} \\
      \addlinespace
      Marks & $m \subseteq \Labels$ \\
      Regular expressions & $r ::= t \mid N_m \mid r \cdot r $ \\
      & \hphantom{$r ::=$}$\mid r + r \mid \epsilon \mid r^{*}$ \\
      Labelled productions & $N -> l : r$ \\
  \end{tabular}
  \captionof{figure}{The abstract syntax of a language definition.}
  \label{fig:input-language-definition}
\end{minipage}\quad
\begin{minipage}{.45\textwidth}
  \centering
  \begin{tabular}{@{}l@{\quad$->$\quad}c@{ $:$\quad}l@{}}
    $E$ & $l$ & \verb|'['| ($E$ (\verb|';'| $E$)$^{*}$ $+$ $\epsilon$) \verb|']'| \\
    $E$ & $a$ & $E$ \verb|'+'| $E$ \\
    $E$ & $m$ & $E_{\{a\}}$ \verb|'*'| $E_{\{a\}}$ \\
    $E$ & $n$ & $N$ \\
  \end{tabular}
  \captionof{figure}{The input language definition used as a running example, an expression language with lists, addition, and multiplication, with precedence defined, but not associativity. Assumes that $N$ matches a numeric terminal.}
  \label{fig:running-example-definition}
\end{minipage}
\end{figure}

@@

\begin{figure}
  \subfloat[$T_D$, the parse trees of $G_D$.\label{fig:running-example-generated:t}]{%
    \begin{tabular}{@{}l@{\quad$->$\quad}c@{$($ }l@{}}
      \toprule
      $E$ & $l$ & \texttt{'['} $(\epsilon + E($\texttt{';'} $E)^{*})$ \texttt{']'} $)$ \\
      $E$ & $a$ & $E$ \texttt{'+'} $E$ $)$ \\
      $E$ & $m$ & $E$ \texttt{'*'} $E$ $)$ \\
      $E$ & $n$ & $N$ $)$ \\
      \bottomrule
    \end{tabular}
  }
  \subfloat[$T'_D$, the parse trees of $G'_D$.\label{fig:running-example-generated:t-prime}]{%
    \begin{tabular}{@{}l@{\quad$->$\quad}c@{$($ }l@{}}
      \toprule
      $E$ & $l$ & \texttt{'['} $(\epsilon + E($\texttt{';'} $E)^{*})$ \texttt{']'} $)$ \\
      $E$ & $a$ & $E$ \texttt{'+'} $E$ $)$ \\
      $E$ & $m$ & $E_{\{a\}}$ \texttt{'*'} $E_{\{a\}}$ $)$ \\
      $E$ & $n$ & $N$ $)$ \\
      $E$ & $g$ & \texttt{'('} $E$ \texttt{')'} $)$ \\
      \midrule
      $E_{\{a\}}$ & $l$ & \texttt{'['} $(\epsilon + E($\texttt{';'} $E)^{*})$ \texttt{']'} $)$ \\
      $E_{\{a\}}$ & $m$ & $E_{\{a\}}$ \texttt{'*'} $E_{\{a\}}$ $)$ \\
      $E_{\{a\}}$ & $n$ & $N$ $)$ \\
      $E_{\{a\}}$ & $g$ & \texttt{'('} $E$ \texttt{')'} $)$ \\
      \bottomrule
    \end{tabular}
  }

  \subfloat[$G_D$, the generated abstract syntax.\label{fig:running-example-generated:w}]{%
    \begin{tabular}{@{}l@{\quad$->$\quad}l@{}}
      \toprule
      $E$ & \texttt{'['} $E_{l1}$ \texttt{']'} \\
      $E$ & $E$ \texttt{'+'} $E$ \\
      $E$ & $E$ \texttt{'*'} $E$ \\
      $E$ & $N$ \\
      \midrule
      $E_{l1}$ & $\epsilon$ \\
      $E_{l1}$ & $E$ $E_{l2}$ \\
      \midrule
      $E_{l2}$ & $\epsilon$ \\
      $E_{l2}$ & \texttt{';'} $E$ $E_{l2}$ \\
      \bottomrule
    \end{tabular}
  }
  \subfloat[$G'_D$, the generated concrete syntax.\label{fig:running-example-generated:w-prime}]{%
    \begin{tabular}{@{}l@{\quad$->$\quad}l@{}}
      \toprule
      $E$ & \texttt{'['} $E_{l1}$ \texttt{']'} \\
      $E$ & $E$ \texttt{'+'} $E$ \\
      $E$ & $E_{\{a\}}$ \texttt{'*'} $E_{\{a\}}$ \\
      $E$ & $N$ \\
      $E$ & \texttt{'('} $E$ \texttt{')'} \\
      \midrule
      $E_{\{a\}}$ & \texttt{'['} $E_{l1}$ \texttt{']'} \\
      $E_{\{a\}}$ & $E_{\{a\}}$ \texttt{'*'} $E_{\{a\}}$ \\
      $E_{\{a\}}$ & $N$ \\
      $E_{\{a\}}$ & \texttt{'('} $E$ \texttt{')'} \\
      \midrule
      $E_{l1}$ & $\epsilon$ \\
      $E_{l1}$ & $E$ $E_{l2}$ \\
      \midrule
      $E_{l2}$ & $\epsilon$ \\
      $E_{l2}$ & \texttt{';'} $E$ $E_{l2}$ \\
      \bottomrule
    \end{tabular}
  }
  \caption{The generated grammars.}
  \label{fig:running-example-generated}
\end{figure}

Examples of elements in each of these four languages can be seen in Fig.~\ref{fig:example-words-in-square}, along with visualizations of the syntax trees. Each element corresponds to the word ``$(1 + 2) * 3$'' in $L(G'_D)$. Note that the word in $L(G_D)$ is ambiguous, and that there are other words in $L(G'_D)$ that correspond to the same element in $L(T_D)$, e.g., ``$((1 + 2)) * 3$'' and ``$(1 + 2) * (3)$''. As a memory aid, the primed versions ($G'_D$ and $T'_D$) contain disambiguation (grouping parentheses, precedence, associativity, etc.) while the unprimed versions ($G_D$ and $T_D$) are the (likely ambiguous) straightforward translations (i.e., ignoring marks) from $D$.

@@

% TODO: (re)make these figures
\begin{figure}
  \subfloat[Example tree in $L(T_D)$ and visualization.\label{fig:sum-add-tree}]{%
    %% \begin{center}
    %% \Tree [.{$m$}
    %%     [.{$a$}
    %%       [.{$n$} \terminal{1} ]
    %%       \terminal{+}
    %%       [.{$n$} \terminal{2} ] ]
    %%     \terminal{*}
    %%     [.{$n$} \terminal{3} ] ]
    %% \end{center}
    $m(a(n(\terminal{1}) \terminal{+} n(\terminal{2})) \terminal{*} n(\terminal{3}))$
  }
  \subfloat[Example tree in $L(T'_D)$ and visualization.]{%
    %% \begin{center}
    %% \Tree [.{$m$}
    %%     [.{$g$}
    %%       \terminal{(}
    %%       [.{$a$}
    %%         [.{$n$} \terminal{1} ]
    %%         \terminal{+}
    %%         [.{$n$} \terminal{2} ] ]
    %%       \terminal{)} ]
    %%     \terminal{*}
    %%     [.{$n$} \terminal{3} ] ]
    %% \end{center}
    $m(g( \terminal{(} a(n( \terminal{1} ) \terminal{+} n( \terminal{2} )) \terminal{)} ) \terminal{*} n( \terminal{3} ))$
  }

  \subfloat[Example word in $L(G_D)$.]{%
    $1 + 2 * 3$
  }
  \subfloat[Example word in $L(G'_D)$.]{%
    $(1 + 2) * 3$
  }
  \caption{Example with elements from each generated language that correspond to each other. The leaf terminals in the tree languages appear underlined to distinguish the two kinds of parentheses.}
  \label{fig:example-words-in-square}
\end{figure}
}

@@

\begin{itemize}
\item $(N, \epsilon, N) \in T$ for all $N \in \NT$.
\item $(N, l, N') \in T$ for all $N' \in L(\labelregex(l))$ where $\labelnt(l) = N$.
\item $(N_1, w_1 \cdot w_2, N_3) \in T$ for all $(N_1, w_1, N_2), (N_2, w_2, N_3) \in T$.
\end{itemize}

@@

\noindent This is useful to us since visibly pushdown automata are closed under difference. Given a pair of trees $t_1$ and $t_2$ we can thus produce a pair of automata recognizing $\words(t_1)$ and $\words(t_2)$ respectively, then construct a pair of automata recognizing $\words(t_1) \setminus \words(t_2)$ and $\words(t_2) \setminus \words(t_1)$, respectively. These new automata recognize the words that are not ambiguous between these two particular trees. Our algorithm thus takes the following shape:

\begin{algorithm}
\caption{The Dynamic Algorithm}
\begin{algorithmic}[1]
\Procedure{Dynamic}{$T$}
  \State $R <- \emptyset$
  \State $U <- \emptyset$
  \ForAll{$t \in T$}
    \State $T' <- T \setminus \{t\}$
    \State $A <- \words(t)$ \Comment{$A$ is a visibly pushdown automaton.}
    \Loop
      \State $A <- A \setminus \bigcup_{t' \in T'} \words(t')$ \Comment{VPDAs closed under difference and union.}
      \If{$L(A) = \emptyset$}
        \State $U <- U \cup \{t\}$
        \State $\textbf{break loop}$
      \EndIf
      \If{$\parse(\shortest(A)) = \{t\}$} \Comment{$\shortest(A)$ denotes a shortest}
        \State $R <- R \cup \{(t, \shortest(A))\}$ \Comment{word recognized by $A$.}
        \State $\textbf{break loop}$
      \EndIf
      \State $T' <- \parse(\shortest(A)) \setminus \{t\}$
    \EndLoop
  \EndFor
  \State $\textbf{return} (R, U)$
\EndProcedure
\end{algorithmic}
\end{algorithm}

>>>>

\newcommand{\RED}[1]{\textcolor{red}{#1}}

@@

Consider this OCaml example of nested \verb|match| expressions, as stated by \cite{palmkvistCreatingDomainSpecificLanguages2019}:

\begin{minipage}{.34\textwidth}
\begin{lstlisting}[language={[objective]caml},numbers=left,basicstyle=\small\tt]
match 1 with
  | 1 -> match "one" with
         | str -> str
  | 2 -> "two"
\end{lstlisting}
\end{minipage}
\vrule
\begin{minipage}{\textwidth}
\begin{lstlisting}[basicstyle=\small\tt]
 File "./nestmatch.ml", line 4, characters 4-5:
 Error: This pattern matches values of type int
        but a pattern was expected which
        matches values of type string
\end{lstlisting}
\end{minipage}

@@

\begin{minipage}{\textwidth}
\begin{lstlisting}[language={[objective]caml},numbers=left,basicstyle=\small\tt]
match 1 with
  | 1 -> (match "one" with
          | str -> str)
  | 2 -> "two"
\end{lstlisting}
\end{minipage}

@@

\begin{itemize}
\item Visibly pushdown languages with the same input partitions
  are closed under intersection, complement, and union
  \cite{alurVisiblyPushdownLanguages2004}. Intersection is given
  by a product automaton. Given a pair of VPDAs
  $(Q_1, \T, \delta_1, q_0, F_1)$ and
  $(Q_2, \T, \delta_2, q'_0, F_2)$ their product automaton has the
  form $(Q_1 \times Q_2, \T, \delta', (q_0, q'_0),$
  $ F_1 \times F_2)$ where, when $c \in \T_c$, $i \in \T_i$ and
  $r \in \T_r$:
  \[
  \begin{array}{r@{\ =\ }l}
    \delta'((p_1, p_2), c, \lambda) & \{((q_1, q_2), (g_1, g_2)) \mid (q_1, g_1) \in \delta_1(p_1, c, \lambda), (q_2, g_2) \in \delta_2(p_2, c, \lambda) \}\\
    \delta'((p_1, p_2), i, \lambda) & \{((q_1, q_2), \lambda) \mid (q_1, \lambda) \in \delta_1(p_1, i, \lambda), (q_2, \lambda) \in \delta_2(p_2, i, \lambda) \}\\
    \delta'((p_1, p_2), r, (g_1, g_2)) & \{((q_1, q_2), \lambda) \mid (q_1, \lambda) \in \delta_1(p_1, r, \lambda), (q_2, \lambda) \in \delta_2(p_2, r, \lambda) \}\\
  \end{array}
  \]

@@

\begin{figure}

\centering
\begin{minipage}{.47\textwidth}
  \centering
  \begin{tabular}{@{}ll@{}}
      Terminals & $t \in \T$ \\
      Non-terminals & $N \in \NT$ \\
      Labels & $l \in \Labels$ \\
      \multicolumn{2}{@{}l@{}}{$\T$, $\NT$, and $\Labels$ disjoint} \\
      \addlinespace
      Marks & $m \subseteq \Labels$ \\
      Regular expressions & $r ::= t \mid N_m \mid r \cdot r $ \\
      & \hphantom{$r ::=$}$\mid r + r \mid \epsilon \mid r^{*}$ \\
      Labelled productions & $N -> l : r$ \\
  \end{tabular}
  \captionof{figure}{The abstract syntax of a language definition.}
  \label{fig:input-language-definition}
\end{minipage}\quad
\begin{minipage}{.45\textwidth}
  \centering
  \begin{tabular}{@{}l@{\quad$->$\quad}c@{ $:$\quad}l@{}}
    $E$ & $l$ & \verb|'['| ($E$ (\verb|';'| $E$)$^{*}$ $+$ $\epsilon$) \verb|']'| \\
    $E$ & $a$ & $E$ \verb|'+'| $E$ \\
    $E$ & $m$ & $E_{\{a\}}$ \verb|'*'| $E_{\{a\}}$ \\
    $E$ & $n$ & $N$ \\
  \end{tabular}
  \captionof{figure}{The input language definition used as a running example, an expression language with lists, addition, and multiplication, with precedence defined, but not associativity. Assumes that $N$ matches a numeric terminal.}
  \label{fig:running-example-definition}
\end{minipage}
\end{figure}

@@

\begin{figure}
  \subfloat[$T_D$, the parse trees of $G_D$.\label{fig:running-example-generated:t}]{%
    \begin{minipage}{0.5\textwidth}
    \centering
    \begin{tabular}{@{}l@{\quad$->$\quad}c@{$($ }l@{}}
      \toprule
      $E$ & $l$ & \texttt{'['} $(\epsilon + E($\texttt{';'} $E)^{*})$ \texttt{']'} $)$ \\
      $E$ & $a$ & $E$ \texttt{'+'} $E$ $)$ \\
      $E$ & $m$ & $E$ \texttt{'*'} $E$ $)$ \\
      $E$ & $n$ & $N$ $)$ \\
      \bottomrule
    \end{tabular}
    \end{minipage}
  }
  \subfloat[$T'_D$, the parse trees of $G'_D$.\label{fig:running-example-generated:t-prime}]{%
    \begin{minipage}{0.5\textwidth}
    \centering
    \begin{tabular}{@{}l@{\quad$->$\quad}c@{$($ }l@{}}
      \toprule
      $E$ & $l$ & \texttt{'['} $(\epsilon + E($\texttt{';'} $E)^{*})$ \texttt{']'} $)$ \\
      $E$ & $a$ & $E$ \texttt{'+'} $E$ $)$ \\
      $E$ & $m$ & $E_{\{a\}}$ \texttt{'*'} $E_{\{a\}}$ $)$ \\
      $E$ & $n$ & $N$ $)$ \\
      $E$ & $g$ & \texttt{'('} $E$ \texttt{')'} $)$ \\
      \midrule
      $E_{\{a\}}$ & $l$ & \texttt{'['} $(\epsilon + E($\texttt{';'} $E)^{*})$ \texttt{']'} $)$ \\
      $E_{\{a\}}$ & $m$ & $E_{\{a\}}$ \texttt{'*'} $E_{\{a\}}$ $)$ \\
      $E_{\{a\}}$ & $n$ & $N$ $)$ \\
      $E_{\{a\}}$ & $g$ & \texttt{'('} $E$ \texttt{')'} $)$ \\
      \bottomrule
    \end{tabular}
    \end{minipage}
  }

  \subfloat[$G_D$, the generated abstract syntax.\label{fig:running-example-generated:w}]{%
    \begin{minipage}{0.5\textwidth}
    \centering
    \begin{tabular}{@{}l@{\quad$->$\quad}l@{}}
      \toprule
      $E$ & \texttt{'['} $E_{l1}$ \texttt{']'} \\
      $E$ & $E$ \texttt{'+'} $E$ \\
      $E$ & $E$ \texttt{'*'} $E$ \\
      $E$ & $N$ \\
      \midrule
      $E_{l1}$ & $\epsilon$ \\
      $E_{l1}$ & $E$ $E_{l2}$ \\
      \midrule
      $E_{l2}$ & $\epsilon$ \\
      $E_{l2}$ & \texttt{';'} $E$ $E_{l2}$ \\
      \bottomrule
    \end{tabular}
    \end{minipage}
  }
  \subfloat[$G'_D$, the generated concrete syntax.\label{fig:running-example-generated:w-prime}]{%
    \begin{minipage}{0.5\textwidth}
    \centering
    \begin{tabular}{@{}l@{\quad$->$\quad}l@{}}
      \toprule
      $E$ & \texttt{'['} $E_{l1}$ \texttt{']'} \\
      $E$ & $E$ \texttt{'+'} $E$ \\
      $E$ & $E_{\{a\}}$ \texttt{'*'} $E_{\{a\}}$ \\
      $E$ & $N$ \\
      $E$ & \texttt{'('} $E$ \texttt{')'} \\
      \midrule
      $E_{\{a\}}$ & \texttt{'['} $E_{l1}$ \texttt{']'} \\
      $E_{\{a\}}$ & $E_{\{a\}}$ \texttt{'*'} $E_{\{a\}}$ \\
      $E_{\{a\}}$ & $N$ \\
      $E_{\{a\}}$ & \texttt{'('} $E$ \texttt{')'} \\
      \midrule
      $E_{l1}$ & $\epsilon$ \\
      $E_{l1}$ & $E$ $E_{l2}$ \\
      \midrule
      $E_{l2}$ & $\epsilon$ \\
      $E_{l2}$ & \texttt{';'} $E$ $E_{l2}$ \\
      \bottomrule
    \end{tabular}
    \end{minipage}
  }
  \caption{The generated grammars.}
  \label{fig:running-example-generated}
\end{figure}

Examples of elements in each of these four languages can be seen in Fig.~\ref{fig:example-words-in-square}, \RED{along with visualizations of the syntax trees}. Each element corresponds to the word ``$(1 + 2) * 3$'' in $L(G'_D)$. Note that the word in $L(G_D)$ is ambiguous, and that there are other words in $L(G'_D)$ that correspond to the same element in $L(T_D)$, e.g., ``$((1 + 2)) * 3$'' and ``$(1 + 2) * (3)$''. As a memory aid, the primed versions ($G'_D$ and $T'_D$) contain disambiguation (grouping parentheses, precedence, associativity, etc.) while the unprimed versions ($G_D$ and $T_D$) are the (likely ambiguous) straightforward translations (i.e., ignoring marks) from $D$.

@@

% TODO: (re)make these figures
\begin{figure}
  \subfloat[Example tree in $L(T_D)$.\label{fig:sum-add-tree}]{% and visualization.]{%
    %% \begin{center}
    %% \Tree [.{$m$}
    %%     [.{$a$}
    %%       [.{$n$} \terminal{1} ]
    %%       \terminal{+}
    %%       [.{$n$} \terminal{2} ] ]
    %%     \terminal{*}
    %%     [.{$n$} \terminal{3} ] ]
    %% \end{center}
    \begin{minipage}{.5\linewidth}
      \centering
      $m(a(n(\terminal{1}) \terminal{+} n(\terminal{2})) \terminal{*} n(\terminal{3}))$
    \end{minipage}
  }
  \subfloat[Example tree in $L(T'_D)$.]{% and visualization.]{%
    %% \begin{center}
    %% \Tree [.{$m$}
    %%     [.{$g$}
    %%       \terminal{(}
    %%       [.{$a$}
    %%         [.{$n$} \terminal{1} ]
    %%         \terminal{+}
    %%         [.{$n$} \terminal{2} ] ]
    %%       \terminal{)} ]
    %%     \terminal{*}
    %%     [.{$n$} \terminal{3} ] ]
    %%   \end{center}
    \begin{minipage}{.5\linewidth}
      \centering
      $m(g( \terminal{(} a(n( \terminal{1} ) \terminal{+} n( \terminal{2} )) \terminal{)} ) \terminal{*} n( \terminal{3} ))$
    \end{minipage}
  }

  \subfloat[Example word in $L(G_D)$.]{%
    \begin{minipage}{.5\linewidth}
      \centering
      $1 + 2 * 3$
    \end{minipage}
  }
  \subfloat[Example word in $L(G'_D)$.]{%
    \begin{minipage}{.5\linewidth}
      \centering
      $(1 + 2) * 3$
    \end{minipage}
  }
  \caption{Example with elements from each generated language that correspond to each other. The leaf terminals in the tree languages appear underlined to distinguish the two kinds of parentheses.}
  \label{fig:example-words-in-square}
\end{figure}
}

@@

\begin{itemize}
\item $(N, \epsilon, N) \in T$ for all $N \in \NT$.
\item $(N, l, N') \in T$ for all $N' \in \NT \cap L(\labelregex(l))$ where $\labelnt(l) = N$.
\item $(N_1, w_1 \cdot w_2, N_3) \in T$ for all $(N_1, w_1, N_2), (N_2, w_2, N_3) \in T$.
\end{itemize}

@@

\noindent This is useful to us since visibly pushdown automata are closed under difference. Given a pair of trees $t_1$ and $t_2$ we can thus produce a pair of automata recognizing $\words(t_1)$ and $\words(t_2)$ respectively, then construct a pair of automata recognizing $\words(t_1) \setminus \words(t_2)$ and $\words(t_2) \setminus \words(t_1)$, respectively. These new automata recognize the words that are not ambiguous between these two particular trees. Our algorithm can thus be seen as Algorithm~\ref{alg:dynamic}.

\begin{algorithm}
\caption{The Dynamic Algorithm}
\label{alg:dynamic}
\begin{algorithmic}[1]
\Procedure{Dynamic}{$T$}
  \State $R <- \emptyset$
  \State $U <- \emptyset$
  \ForAll{$t \in T$}
    \State $T' <- T \setminus \{t\}$
    \State $A <- \words(t)$ \Comment{$A$ is a visibly pushdown automaton.}
    \Loop
      \State $A <- A \setminus \bigcup_{t' \in T'} \words(t')$ \Comment{VPDAs closed under difference and union.}
      \If{$L(A) = \emptyset$}
        \State $U <- U \cup \{t\}$
        \State $\textbf{break loop}$
      \EndIf
      \If{$\parse(\shortest(A)) = \{t\}$} \Comment{$\shortest(A)$ denotes a shortest}
        \State $R <- R \cup \{(t, \shortest(A))\}$ \Comment{word recognized by $A$.}
        \State $\textbf{break loop}$
      \EndIf
      \State $T' <- \parse(\shortest(A)) \setminus \{t\}$
    \EndLoop
  \EndFor
  \State $\textbf{return} (R, U)$
\EndProcedure
\end{algorithmic}
\end{algorithm}
